---
title: "Practice-6.3"
author: "Wei-Ting Sun"
date: "2024-11-10"
output: html_document
---

### Lotka-Volterra function

At first, I tried to fix the wrong code about the Lotka-Volterra function.
To confirm that both 2 lines of species works whether competition exists, I set 2 variables `sp1` and `sp2`, which represented 2 species. 

```{r, warning=FALSE, message=FALSE}
Lotka_Volterra <- function(sp1, sp2){
  num_gen<-30
  N1 <- rep(0,30)
  N2 <- rep(0,30)
  generation<-1:num_gen
  growth.rate<-1.2
  K1<-100
  K2<-120
  a12<-0.8
  a21<-0.8
  N1[1]<-sp1
  N2[1]<-sp2
  for (i in 2:30)  {
    N1[i] = N1[i-1] + (growth.rate* N1[i-1] * ((K1-N1[i-1]-(a12*N2[i-1]))/K1))
    N2[i] = N2[i-1] + (growth.rate* N2[i-1] * ((K2-N2[i-1]-(a21*N1[i-1]))/K2))
  }
  plot(N1~generation,typ="b", col="blue",xlim=c(0,30),ylim=c(0,max(c(K1,K2))),ylab="N")
  lines(N2~generation,typ="b", col="red", pch=22, lty=2)
  legend("topleft",legend=c("species1","species2"), col=c("blue","red"),
         pch=21:22, lty=1:2)
  }
```

Use `compLV` from the package `EcoVirtual` to check the result.
(I cannot show the plot made by `compLV`...)

```{r, warning=FALSE, message=FALSE}
Lotka_Volterra(1,0)
Lotka_Volterra(0,1)
Lotka_Volterra(1,1)

library(EcoVirtual)
compLV(1,0,30,1.2,1.2,100,120,0.8,0.8)
compLV(0,1,30,1.2,1.2,100,120,0.8,0.8)
compLV(1,1,30,1.2,1.2,100,120,0.8,0.8)
```

Change the function slightly to create `Lotka_Volterra2`, which use `growth.rate` as variable.

```{r, warning=FALSE, message=FALSE}
Lotka_Volterra2 <- function(growth.rate){
  num_gen<-30
  N1 <- rep(0,30)
  N2 <- rep(0,30)
  generation<-1:num_gen
  K1<-100
  K2<-120
  a12<-0.8
  a21<-0.8
  N1[1]<-1
  N2[1]<-1
  for (i in 2:30)  {
    N1[i] = N1[i-1] + (growth.rate* N1[i-1] * ((K1-N1[i-1]-(a12*N2[i-1]))/K1))
    N2[i] = N2[i-1] + (growth.rate* N2[i-1] * ((K2-N2[i-1]-(a21*N1[i-1]))/K2))
  }
  plot(N1~generation,typ="b", col="blue",xlim=c(0,30),ylim=c(0,max(c(K1,K2))),
       ylab="N",main=paste("Rate =", growth.rate))
  lines(N2~generation,typ="b", col="red", pch=22, lty=2)
  legend("topleft",legend=c("species1","species2"), col=c("blue","red"),
         pch=21:22, lty=1:2)
}
```

### Save GIF
Time to make an animation!
```{r, warning=FALSE, message=FALSE}
library(animation)
saveGIF({
  for (j in seq(0.5,1.5,by=0.1)){
    Lotka_Volterra2(j)
  }})
```